---
title: "Stage lighting arrangements"
date: today
format:
  html:
    embed-resources: true
---
```{r}
#| label: load-packages
#| include: false
devtools::load_all()
options(warn = 0)
```
## Stage 1

- 7mx7m stage
- 2 chandeliers
  - 15 candles
  - 0.6m diameter
  - centred 2m from side of stage, over front edge of stage

Assumptions:

- Lux values shown for 1m distance (assuming 3m high and actors 2m tall, lux is at roughly head height)
- Candles 10cm tall, 10 lumens (10/4π lumens used to calculate lux at a point)
- Candles placed equidistant from each other around chandelier
  
```{r}
#| echo: false
stage_1 <- stage$new(width = 700, depth = 700, unit_scaling = 20)

stage_1$add_candelabra(x = 200, y = 0, n = 15, r = 30, h = 100)
stage_1$add_candelabra(x = 500, y = 0, n = 15, r = 30, h = 100)

stage_1$plot_light()
```

## Stage 2

As above, but with the chandeliers fully over the stage

```{r}
#| echo: false
stage_2 <- stage$new(width = 700, depth = 700, unit_scaling = 20)

stage_2$add_candelabra(x = 200, y = 60, n = 15, r = 30, h = 100)
stage_2$add_candelabra(x = 500, y = 60, n = 15, r = 30, h = 100)

stage_2$plot_light()
```

## Stage 3

As stage 1, with two extra chandeliers.

```{r}
#| echo: false
stage_3 <- stage$new(width = 700, depth = 700, unit_scaling = 20)

stage_3$add_candelabra(x = 200, y = 0, n = 15, r = 30, h = 100)
stage_3$add_candelabra(x = 500, y = 0, n = 15, r = 30, h = 100)
stage_3$add_candelabra(x = 200, y = 300, n = 15, r = 30, h = 100)
stage_3$add_candelabra(x = 500, y = 300, n = 15, r = 30, h = 100)

stage_3$plot_light()
```

## Stage 4

As stage 2, with two extra chandeliers (the same distance away from the front two chandeliers, so further back on the stage).

```{r}
#| echo: false
stage_4 <- stage$new(width = 700, depth = 700, unit_scaling = 20)

stage_4$add_candelabra(x = 200, y = 60, n = 15, r = 30, h = 100)
stage_4$add_candelabra(x = 500, y = 60, n = 15, r = 30, h = 100)
stage_4$add_candelabra(x = 200, y = 360, n = 15, r = 30, h = 100)
stage_4$add_candelabra(x = 500, y = 360, n = 15, r = 30, h = 100)

stage_4$plot_light()
```

