---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# lumos

<!-- badges: start -->
![lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange)
![version: 0.0.0.9000](https://img.shields.io/badge/version-0.0.0.9000-blueviolet)
<!-- badges: end -->

{lumos} is an R package and shiny app that enable exploration of stage lighting in candelit theatres and how different configurations affect the light levels across different areas of the stage.

## Installation

You can install the development version of lumos from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("chrisbrownlie/lumos")
```

## Lighting app

You can launch the lumos app with the code below, or visit it at chrisbrownlie.com/lumos (not yet available).

```{r launchapp, eval = FALSE}
library(lumos)

lumos::run_app()
```

## Contact
For more information, contact [Chris Brownlie](chris.brownlie@hotmail.co.uk)
